---
  title: "CFE Initial Exploration"
  output: html_document
---

```{r results='hide', message=FALSE, warning=FALSE}


#Libraries
library(tidyverse)
library(rmarkdown)
library(RODBC)
library(RODBCext)
library(optparse)
library(data.table)
library(Matrix)
library(outliers)
library(plyr)
library(dplyr)
library(reshape2)
library(pastecs)
library(ggmap)
library(plotly)

library(rgeos)
library(sp)


```
###### Set your database connection info

```{r results='hide', message=FALSE, warning=FALSE}

server <- "USINTERN13\\SQLEXPRESS"
database <-"test1"
#startDate <- "20160101" 
#endDate <- "20170202"
```

###### Reads in unique 108 zones


```{r results='hide', message=FALSE, warning=FALSE}
allNames <- as.data.frame(read.csv("C:/Users/sspinetto/Desktop/allnames.csv", stringsAsFactors = FALSE))

allLats <- as.data.frame(read.csv("C:/Users/sspinetto/Desktop/weatherStationList.csv", stringsAsFactors = FALSE))


f <- function(s) strsplit(s, "_")
names <-sapply(allNames, f)

uniqueNames <- colsplit(allNames$mx_cfe_manzanillo_one_load_act, pattern="_", names = c("0","1","name","4","5","6"))

finalNames <- unique(uniqueNames$name)
finalNames[[53]]<- "acapulco"
finalNames<- sort(finalNames)

```


##### This is the function that gets the % of non zeroes for each load type, later it is looped through for each zone


```{r results='hide', message=FALSE, warning=FALSE}


getMyZeros <- function (server, database, finalNames) {

tryCatch({ 
  
necName <- finalNames
  
fileName1 <- paste0("mx_cfe_",necName)
  
#set connection
setServ <- paste0("driver={SQL Server};server=",server,";database=",database,";trusted_connection=true")
myServer <- odbcDriverConnect(setServ)

# perform queries to zero, one, two, three
query0 <- paste0("select date,time,load_act from ",fileName1,"_zero_load_act"
 #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
                 )
load0 <-  sqlQuery(myServer,query0)


query1 <- paste0("select date,time,load_act from ",fileName1,"_three_load_act"
                 #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
)
load3 <-  sqlQuery(myServer,query1)

query2 <- paste0("select date,time,load_act from ",fileName1,"_two_load_act"
                 #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
)
load2 <-  sqlQuery(myServer,query2)

query3 <- paste0("select date,time,load_act from ",fileName1,"_one_load_act"
                 #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
)
load1 <-  sqlQuery(myServer,query3)


# trunc for compare
trunc0 <- head(load0, -4872)
trunc1 <- head(load1, -3864)
trunc2 <- head(load2, -2520)
trunc3 <- load3


#combine

fullLoad <- as.data.frame(cbind(trunc0,trunc1,trunc2,trunc3))


colnames(fullLoad) <- c("date_0", "time_0", "load_act_0","date_1", "time_1", "load_act_1","date_2", "time_2", "load_act_2",
                        "date_3", "time_3", "load_act_3")
                      
## sanity check to make sure columns align
# 
# head(fullLoad)

## clean up


compareLoad <- data.frame(fullLoad$date_0,fullLoad$time_0,fullLoad$load_act_0,
                          fullLoad$load_act_1,fullLoad$load_act_2,fullLoad$load_act_3)


zeroPercent0 <- mean(!compareLoad$fullLoad.load_act_0)
zeroPercent1 <- mean(!compareLoad$fullLoad.load_act_1)
zeroPercent2 <- mean(!compareLoad$fullLoad.load_act_2)
zeroPercent3 <- mean(!compareLoad$fullLoad.load_act_3)


zeroVector <- c(zeroPercent0,zeroPercent1,zeroPercent2,zeroPercent3)
# 
# print (zeroPercent0)
# print (zeroPercent1)
# print (zeroPercent2)
# print (zeroPercent3)


### lets find the differences

compareLoad$dif0to1 <- compareLoad$fullLoad.load_act_0 - compareLoad$fullLoad.load_act_1
compareLoad$dif1to2 <- compareLoad$fullLoad.load_act_1 - compareLoad$fullLoad.load_act_2
compareLoad$dif2to3 <- compareLoad$fullLoad.load_act_2 - compareLoad$fullLoad.load_act_3
compareLoad$dif0to3 <- compareLoad$fullLoad.load_act_0 - compareLoad$fullLoad.load_act_3




summary(compareLoad$dif0to1)
summary(compareLoad$dif1to2)
summary(compareLoad$dif2to3)
summary(compareLoad$dif0to3)
}, error= function(e){})
return(zeroVector)
}

```

##### here we have our function to get summaries

```{r results='hide', message=FALSE, warning=FALSE}


getMySummaries <- function (server, database, finalNames) {
  
  tryCatch({ 
    

    
    fileName1 <- paste0("mx_cfe_", finalNames)
    
    #set connection
    setServ <- paste0("driver={SQL Server};server=",server,";database=",database,";trusted_connection=true")
    myServer <- odbcDriverConnect(setServ)
    
    # perform queries to zero, one, two, three
    query0 <- paste0("select date,time,load_act from ",fileName1,"_zero_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load0 <-  sqlQuery(myServer,query0)
    
    
    query1 <- paste0("select date,time,load_act from ",fileName1,"_three_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load3 <-  sqlQuery(myServer,query1)
    
    query2 <- paste0("select date,time,load_act from ",fileName1,"_two_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load2 <-  sqlQuery(myServer,query2)
    
    query3 <- paste0("select date,time,load_act from ",fileName1,"_one_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load1 <-  sqlQuery(myServer,query3)
    
    
    # trunc for compare
    trunc0 <- head(load0, -4872)
    trunc1 <- head(load1, -3864)
    trunc2 <- head(load2, -2520)
    trunc3 <- load3
    
    
    #combine
    
    fullLoad <- as.data.frame(cbind(trunc0,trunc1,trunc2,trunc3))
    
    
    colnames(fullLoad) <- c("date_0", "time_0", "load_act_0","date_1", "time_1", "load_act_1","date_2", "time_2", "load_act_2",
                            "date_3", "time_3", "load_act_3")
    
    ## sanity check to make sure columns align
    # 
    # head(fullLoad)
    
    ## clean up
    
    
    compareLoad <- data.frame(fullLoad$date_0,fullLoad$time_0,fullLoad$load_act_0,
                              fullLoad$load_act_1,fullLoad$load_act_2,fullLoad$load_act_3)
    
    
    zeroPercent0 <- mean(!compareLoad$fullLoad.load_act_0)
    zeroPercent1 <- mean(!compareLoad$fullLoad.load_act_1)
    zeroPercent2 <- mean(!compareLoad$fullLoad.load_act_2)
    zeroPercent3 <- mean(!compareLoad$fullLoad.load_act_3)
    
    
    zeroVector <- c(zeroPercent0,zeroPercent1,zeroPercent2,zeroPercent3)
    # 
    # print (zeroPercent0)
    # print (zeroPercent1)
    # print (zeroPercent2)
    # print (zeroPercent3)
    
    
    ### lets find the differences
    
    compareLoad$dif0to1 <- compareLoad$fullLoad.load_act_0 - compareLoad$fullLoad.load_act_1
    compareLoad$dif1to2 <- compareLoad$fullLoad.load_act_1 - compareLoad$fullLoad.load_act_2
    compareLoad$dif2to3 <- compareLoad$fullLoad.load_act_2 - compareLoad$fullLoad.load_act_3
    compareLoad$dif0to3 <- compareLoad$fullLoad.load_act_0 - compareLoad$fullLoad.load_act_3
    
    
  
    
    mean01 <- summary(load0$load_act)
    
    sumVector <- mean01
    
  }, error= function(e){})
  return(sumVector)
}

```
#### third function to get something else :P

```{r}
getMyOther <- function (server, database, finalNames) {
  
  tryCatch({ 
    

    
    fileName1 <- paste0("mx_cfe_", finalNames)
    
    #set connection
    setServ <- paste0("driver={SQL Server};server=",server,";database=",database,";trusted_connection=true")
    myServer <- odbcDriverConnect(setServ)
    
    # perform queries to zero, one, two, three
    query0 <- paste0("select date,time,load_act from ",fileName1,"_zero_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load0 <-  sqlQuery(myServer,query0)
    
    
    query1 <- paste0("select date,time,load_act from ",fileName1,"_three_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load3 <-  sqlQuery(myServer,query1)
    
    query2 <- paste0("select date,time,load_act from ",fileName1,"_two_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load2 <-  sqlQuery(myServer,query2)
    
    query3 <- paste0("select date,time,load_act from ",fileName1,"_one_load_act"
                     #     ," where date > ",startDate," AND date < ", endDate   #uncomment this line if using custom date set 
    )
    load1 <-  sqlQuery(myServer,query3)
    
    
    # trunc for compare
    trunc0 <- head(load0, -4872)
    trunc1 <- head(load1, -3864)
    trunc2 <- head(load2, -2520)
    trunc3 <- load3
    
    
    #combine
    
    fullLoad <- as.data.frame(cbind(trunc0,trunc1,trunc2,trunc3))
    
    
    colnames(fullLoad) <- c("date_0", "time_0", "load_act_0","date_1", "time_1", "load_act_1","date_2", "time_2", "load_act_2",
                            "date_3", "time_3", "load_act_3")
    
    ## sanity check to make sure columns align
    # 
    # head(fullLoad)
    
    ## clean up
    
    
    compareLoad <- data.frame(fullLoad$date_0,fullLoad$time_0,fullLoad$load_act_0,
                              fullLoad$load_act_1,fullLoad$load_act_2,fullLoad$load_act_3)
    
    
    

    ### lets find the differences
    
    compareLoad$dif0to1 <- compareLoad$fullLoad.load_act_0 - compareLoad$fullLoad.load_act_1
    compareLoad$dif1to2 <- compareLoad$fullLoad.load_act_1 - compareLoad$fullLoad.load_act_2
    compareLoad$dif2to3 <- compareLoad$fullLoad.load_act_2 - compareLoad$fullLoad.load_act_3
    compareLoad$dif0to3 <- compareLoad$fullLoad.load_act_0 - compareLoad$fullLoad.load_act_3
    
  
    
    difVector <- data_frame(compareLoad$fullLoad.date_0, compareLoad$fullLoad.time_0,
                            compareLoad$fullLoad.load_act_0,compareLoad$fullLoad.load_act_1,compareLoad$fullLoad.load_act_2,
                            compareLoad$fullLoad.load_act_3,
                            compareLoad$dif0to1,compareLoad$dif1to2,compareLoad$dif2to3,compareLoad$dif0to3)
    
    check01<- intersect(difVector$`compareLoad$fullLoad.load_act_0`,difVector$`compareLoad$fullLoad.load_act_1`)
    check01<- intersect(difVector$`compareLoad$fullLoad.load_act_0`,difVector$`compareLoad$fullLoad.load_act_1`)
    check01<- intersect(difVector$`compareLoad$fullLoad.load_act_0`,difVector$`compareLoad$fullLoad.load_act_1`)
     length(check)
    
    
    
    
  }, error= function(e){})
 
  return(difVector)
}


```



##### First Loop, Calculates Non Zeroes


```{r,warning=FALSE}

loop_zero_data <- vector("list", length(finalNames))

for(x in seq_along(finalNames)){
  
  loop_zero_data[[x]] <- getMyZeros(server,database,finalNames[[x]])
}

names(loop_zero_data) <- finalNames

### prints % of zeroes in each data set, load0, load1, load2, load3

head(loop_zero_data)

```

#####second Loop calculates summaries

```{r, warning= FALSE}

loop_sum_data <- vector("list", length(finalNames))

for(x in seq_along(finalNames)){
  
  loop_sum_data[[x]] <- getMySummaries(server,database,finalNames[[x]])
}
names(loop_sum_data) <- finalNames

### prints % of zeroes in each data set, load0, load1, load2, load3

head(loop_sum_data)

```


###third loop 4 for differences between 01, 12, 23, 03
```{r, warning=FALSE}

loop_dif_data <- vector("list", length(finalNames))

for(x in seq_along(finalNames)){
  
  loop_dif_data[[x]] <- getMyOther(server,database,finalNames[[x]])
}
names(loop_dif_data) <- finalNames





```

#### Put Summary Data in Table 4 plotting

```{r, warning=FALSE}

  getMedian <- ldply(loop_sum_data)
  
  plot_ly(getMedian, y= ~Median, type='scatter', mode='markers', text= ~.id)

```

#### lets see what else we can visualize that's useful.....

```{r, message=FALSE,warning=FALSE}



lookupNames <- sapply(finalNames, paste0, " Mexico")
lookupNames2<- sapply(allLats$stationname, paste0, "Mexico")
lonlat <- geocode(lookupNames) 
set1<- data.frame(p1=lonlat$lon,p2=lonlat$lat)
lonlat2<-geocode(lookupNames2)
set2<- data.frame(p1=lonlat2$lon,p2=lonlat2$lat)
cities <- cbind(finalNames, lonlat)

allLats <- as.data.frame(read.csv("C:/Users/sspinetto/Desktop/magicMaker.csv", stringsAsFactors = FALSE))



f <- function(s) strsplit(s, split = "(?<=[a-zA-Z])\\s*(?=[0-9])", perl = TRUE)
names <-as.data.frame(sapply(allLats$cities, f))


final_df <- as.data.frame(t(names))

uniqueLats <- colsplit(final_df$V2, pattern=" ", names = c("lat","long"))
#cities2 <- cbind(uniqueLats$name,uniqueLats$lat,uniqueLats$long)
latlongs2<- as.data.frame(cbind(uniqueLats$lat,uniqueLats$long))


library(devtools)
install_github("dkahle/ggmap")
library(ggmap)

myPlace <- "Moscow"
    myZoom <- 5
    

    myMap <- get_map(location=c(lon = mean(latlongs2$V2), lat = mean(latlongs2$V1)) , zoom= 5, maptype="satellite", scale = 2)
    mapper <- ggmap(myMap)
    
    mapper+ geom_point(data=latlongs2, aes(x=V2, y=V1), size=2,colour= "red")
    #+geom_text(data =cities,aes(label=.id),hjust=0, vjust=0, size=2)
    
    
    

```

###What's next !? -- lets find closest weather station to each!

```{r}

distp1p2 <- function(p1,p2) {
    dst <- sqrt((p1[1]-p2[1])^2+(p1[2]-p2[2])^2)
    return(dst)
}

dist2b <- function(y) which.min(apply(set2, 1, function(x) min(distp1p2(x,y))))
bestStation<- apply(set1, 1, dist2b)


stationKey<- data.frame(allLats$stationid,allLats$stationname)


head(bestStation)
head(stationKey)


```

